\section{Conclusion}

At the end of all of this, I am not entirely sure what I could share as a conclusion.
I know that I greatly enjoyed spending this time finding and reading the literature I have because I am now much more familiar with the technologies involved with anti-aliasing, and rendering a scene in general.
(I also came across some other concepts not directly related to anti-aliasing that are rather interesting too.) I do wish I could give you better performance data than I have, but at the same time I doubt it would differ from what any of us would expect for these methods.

This much I will also say: I would actually like to see more transparency concerning anti-aliasing in games.
By that I mean clearly identifying the technique used, and not just labelling the setting 'Anti-Aliasing' combined with options ranging from 'Low' to 'High,' for example.
The use of 'Low' to 'High' for the options is not that bad though, at least in some contexts such as in \textit{Serious Sam Fusion 2017} with FXAA as these options potentially relate to the method's presets.
It is more the combination of generic 'Anti-Aliasing' with equally generic 'Ultra' that I am being critical of.

Though not something that needs to be given in-game, I would appreciate it being publicly shared what filter is being used for the samples of rasterization-based methods of MSAA and SSAA in games.
This is more to satisfy my own curiosity though.
If a custom sampling pattern is being used, that being shared would also be appreciated, though I suspect that is not very common.

